State of the Practice for Medical Imaging Software

### 2022-10-31 StateOfPractice/Papers/MedImageSoft_SOP-arXiv/MedImageSoft_SOP.tex
Edits to the Comparision to Artifacts section

\item \textbf{A Developer Code of Conduct} explicitly states the expectations
for developers on how they should treat one another \citep{TouraniEtAl2017}. The
code outlines rules for communication and establishes enforcement mechanisms for
violations.  As \citet{TouraniEtAl2017} states, the code of conduct documents
the spirit of a community so that anyone can comfortably contribute regardless
of ethnicity, gender, or sexual orientation. Three popular code's of conduct are
\citep{TouraniEtAl2017}:
\href{https://www.contributor-covenant.org/version/2/1/code_of_conduct/}
{Contributor Covenant}, \href{https://ubuntu.com/community/code-of-conduct}
{Ubuntu Code of Conduct}, and \href{https://www.djangoproject.com/conduct/}
{Django Code of Conduct}. A code of conduct can improve inclusivity, which
brings the benefit of a wider pool of contributors.  For example, a code of
conduct can improve the participation of women \citep{SinghEtAl2021}. A standard
of ethical behaviour can be captured in the code, for projects that are looking
to abide by a code of ethics, such as the IEEE Code of Ethics \citep{IEEE1999},
or the Professional Engineers of Ontario code of ethics \citep[p.\
23--24]{PEO2021}.

@@

\begin{itemize}
	\item Represent the design using Unified Modelling Language class diagrams.
	This approach is suited to object-oriented design and designs that use
	patterns \citep{Gamma1995}.
	\item Rigorously document the design following the template for a Module
	Guide (MG) \citep{ParnasEtAl1984}.  An MG organizes the modules in a
	hierarchy by their secrets.
	\item Explain the design using data flow diagrams to show typical use cases
	for input transformation.
	\item Traceability
	\item Using a textual description, list for each module (or class), the
	state variables (if any), exported constants and all exported access
	programs.  This shows the interface that can used to access each module's
	services.
	\item Document the Module Interface Specification (MIS)
	\citep{HoffmanAndStrooper1995}. An MIS is an abstract model that formally
	shows each module's access programs and the associated transitions and
	outputs based on their state, environment, and input variables
	\citep{ElSheikhEtAl2004, SmithAndYu2009}.
\end{itemize}

@@

\item \textbf{A test plan} Verification involves checking that the governing
equations for the model, together with other definitions, including boundary
and/or initial conditions, are solved correctly.  Validation, on the other hand,
involves checking that the model is close enough to reality for whatever
scientific or engineering problem is being addressed by the software.
Verification is an exercise in mathematics, while validation is an exercise in
engineering and science~\cite[p.~24]{Roache1998}.  Verification is not just
important for the code.  As shown by the IEEE Standard for Software Verification
and Validation Plans~\cite[p.\ 412]{VanVliet2000}, V\&V activities are
recommended for each phase of the software development lifecycle.

@@

The above discussion shows that, taken together, MI projects fall somewhat short
of recommended best practices for research software.  However, MI software is
not alone in this.  Many, if not most, research projects fall short of best
practices.  A gap exists in scientific computing development practices and
software engineering recommendations \citep{Storer2017, Kelly2007,
OwojaiyeEtAl2021_CSE}. \citet{JohansonAndHasselbring2018} observe that the
state-of-the-practice for research software in industry and academia does not incorporate
state-of-the-art SE tools and methods.  This causes sustainability and
reliability problems \citep{FaulkEtAl2009}. Rather than benefit from capturing
and reusing previous knowledge, projects waste time and energy ``reinventing the
wheel'' \citep{deSouzaEtAl2019}.

>>>>

\item \textbf{A Developer Code of Conduct} explicitly states the expectations
for developers on how they should treat one another \citep{TouraniEtAl2017}. The
code outlines rules for communication and establishes enforcement mechanisms for
violations.  As \citet{TouraniEtAl2017} states, the developer code documents
the spirit of a community so that anyone can comfortably contribute regardless
of ethnicity, gender, or sexual orientation. Three popular codes of conduct are
\citep{TouraniEtAl2017}:
\href{https://www.contributor-covenant.org/version/2/1/code_of_conduct/}
{Contributor Covenant}, \href{https://ubuntu.com/community/code-of-conduct}
{Ubuntu Code of Conduct}, and \href{https://www.djangoproject.com/conduct/}
{Django Code of Conduct}. A code of conduct can improve inclusivity, which
brings the benefit of a wider pool of contributors.  For example, a code of
conduct can improve the participation of women \citep{SinghEtAl2021}. A standard
of ethical behaviour can be captured in the code, for projects that are looking
to abide by a code of ethics, such as the IEEE Code of Ethics \citep{IEEE1999},
or the Professional Engineers of Ontario code of ethics \citep[p.\
23--24]{PEO2021}.

@@

\begin{itemize}
	\item Representation of the system design and class design using Unified
	Modelling Language class diagrams. This approach is suited to
	object-oriented design and designs that use patterns \citep{Gamma1995}.
	\item Rigorous documentation of the system design following the template for
	a Module Guide (MG) \citep{ParnasEtAl1984}.  An MG organizes the modules in
	a hierarchy by their secrets.
	\item An explanation of the design using data flow diagrams to show typical use cases
	for input transformation.
	\item A table or graph showing the traceability between the requirements and
	the modules (or classes)
	\item The syntax of the modules (or classes) by providing lists of the state
	variables, exported constants and all exported access programs for each
	module (or class).  This shows the interface that can used to access each
	module's services.
	\item A formal specification of the semantics of input/output relationships
	and state transitions for each module using a Module Interface Specification
	(MIS) \citep{HoffmanAndStrooper1995}. An MIS is an abstract model that
	formally shows each module's access programs and the associated transitions
	and outputs based on their state, environment, and input variables.
	\citet{ElSheikhEtAl2004, SmithAndYu2009} show the example of an MIS for a
	mesh generator.
\end{itemize}

@@

\item \textbf{A Test Plan} describes the scope, approach, resources, and the
schedule of planned test activities \citep{VanVliet2000}.  The plan should cover
details such as the makeup of the testing team, automated testing tools and
technology to employ, the testing process, system tests, integration tests and
unit tests.  A test plan can also include the specific plans for peer code (and
documentation) review, as discussed further in Section~\ref{Sec_PeerReview}.

@@

The above discussion shows that, taken together, MI projects fall somewhat short
of recommended best practices for research software.  However, MI software is
not alone in this.  Many, if not most, research projects fall short of best
practices.  A gap exists in research software development practices and software
engineering recommendations \citep{Storer2017, Kelly2007, OwojaiyeEtAl2021_CSE}.
\citet{JohansonAndHasselbring2018} observe that the state-of-the-practice for
research software in industry and academia does not incorporate state-of-the-art
SE tools and methods.  This causes sustainability and reliability problems
\citep{FaulkEtAl2009}. Rather than benefit from capturing and reusing previous
knowledge, projects waste time and energy ``reinventing the wheel''
\citep{deSouzaEtAl2019}.
